SMT-COMP 2022\\ 17th International Satisfiability Modulo Theory Competition

### 2022-08-12 2022/slides/smtWorkshop/slides.tex
fixes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   SMT-COMP 2021 - Presentation on SMT-Workshop
%                   virtual conference in "Los Angeles"
%
%   1 hour
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%% Titel, Autor und Datum des Vortrags:
\title{SMT-COMP 2021\\
17th International Satisfiability Modulo Theory Competition}
\author{\emph{Haniel Barbosa} \and Jochen Hoenicke \and Fran\c{c}ois Bobot}
\date{Aug 11, 2022}

@@

\begin{frame}[fragile]{SMT-COMP Tracks (traditional)}
  \emph{Single Query Track}
  \begin{itemize}
  \item Determine satisfiability of one problem
  \item Solver answers sat/unsat/unknown
  \end{itemize}
  \medskip

@@

@@

@@

  \pause
  \emph{Unsat Core}
  \begin{itemize}
  \item \emph{Bitwuzla}: {\small QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}
  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith, Bitvec, Equality, Equality+LinearArith, Equality+MachineArith, Equality+NonLinearArith, FPArith, QF\_Equality, QF\_Equality+NonLinearArith, QF\_LinearIntrArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith \end{minipage}
  \item \emph{Yices2}: {\small QF\_Equality+LinearArith, QF\_LinearRealArith}
  \end{itemize}

@@

\begin{frame}{Division Winners}
  \emph{Incremental}
  \begin{itemize}
\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith,EqualityNonLinearArith,Equality
\item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
\item \emph{Bitwuzla}: FPArith, QF\_Bitvec, QF\_FPArith
\item \emph{Yices2}: QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
\item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
\item \emph{OpenSMT}: QF\_LinearRealArith
  \end{itemize}
  \medskip

@@

  \begin{itemize}
  \item  instances of 391\,363 have no status

@@

  \vitem We had only three solvers with soundness issues: SMTIinterpol, Z3++,
  yices-ismt
  \begin{itemize}
    \item Down from 10 last year
  \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{SMT-COMP organizing committee}
  Three people organize the SMT-COMP.  In 2021:
  \begin{itemize}
  \item Haniel Barbosa
  \item Jochen Hoenicke
  \item Fran\c{c}ois Bobot
  \end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   SMT-COMP 2022 - Presentation on SMT-Workshop
%                   virtual conference in "Los Angeles"
%
%   1 hour
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%% Titel, Autor und Datum des Vortrags:
\title{SMT-COMP 2022\\
17th International Satisfiability Modulo Theory Competition}
\author{\emph{Haniel Barbosa} \and Jochen Hoenicke \and Fran\c{c}ois Bobot}
\date{Aug 11, 2022}

@@

\begin{frame}[fragile]{SMT-COMP Tracks (traditional)}
  \emph{Single Query (SQ) Track}
  \begin{itemize}
  \item Determine satisfiability of one problem
  \item Solver answers sat/unsat/unknown
  \end{itemize}
  \medskip

@@

\medskip
\pause
  \emph{This year} the sat/unsat results from sound solvers in SQ were used to
  include benchmarks on the MV, UC and PE tracks.

@@

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-smtrat.pdf}}
\end{frame}
}

@@

  \pause
  \emph{Unsat Core}
  \begin{itemize}
\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith, Equality+MachineArith,Equality+NonLinearArith,Equality(Seq), QF\_Datatypes
\item \emph{Vampire}: Equality(Par)
\item \emph{Bitwuzla}: QF\_EqualityBitvec, QF\_FPArith
\item \emph{Yices2}: QF\_Bitvec, QF\_Equality+LinearArith, QF\_Equality, QF\_LinearIntArith, QF\_LinearRealArith
\item \emph{SMTInterpol}: QF\_Equality+NonLinearArith
\item \emph{UltimateEliminator+MathSAT}: FPArith

@@

\begin{frame}{Division Winners}
  \emph{Incremental}
  \begin{itemize}
\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith,EqualityNonLinearArith,Equality
\item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
\item \emph{Bitwuzla}: FPArith, QF\_FPArith
\item \emph{Yices2}: QF\_Bitvec, QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
\item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
\item \emph{OpenSMT}: QF\_LinearRealArith
  \end{itemize}
  \medskip

@@

  \begin{itemize}
  \item  111\,451 instances of 391\,363 have no status

@@

  \vitem We had only three solvers with soundness issues: SMTIinterpol, Z3++,
  yices-ismt
  \begin{itemize}
    \item Down from 10 last year
    \pause
    {\tiny (but note that this may be because of our issue with ignoring most of the
    new benchmarks in the selection)}

  \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{SMT-COMP organizing committee}
  Three people organize the SMT-COMP.  In 2022:
  \begin{itemize}
  \item Haniel Barbosa
  \item Jochen Hoenicke
  \item Fran\c{c}ois Bobot
  \end{itemize}
